% vim:ft=tex

\section{Conclusions and Outlook}

All goals which we described in chapter \ref{tasks} for the first part of the project could reached. We installed and configured Nominatim as well as its components. Furthermore we compared different Hadoop distributions and installed the \acs{hdp}. The data engineering part could be successfully completed as well. The data was profiled and a dataset was stored. Moreover we could identify difficulties and try to find solutions for those. During the implementation several issues occurred. For example we struggled with getting all postalcodes together because they aren`t provided carefully on web sources. There have been always some countries missing. Therefore we collect zipcodes directly out of PostgresDB. Further issues happened during the installation of Nominatim and \acs{hdp} could have been fixed by the team. One more issue occurred by initializing Graphhopper. It turned out that the virtual machine we are using ran out of space. This is an issue which is about to be fixed. But not just hardware and software could lead to inefficiency, also bad teamwork could lead to this. Since the team members were totally new to each other and were used to different languages and working manners, the communication in the beginning wasn't`t easy, but during the project the team made a big process. Apart from daily scrums we met once a week extra to work as a team together what makes the work immensely easier. It also gives everyone the chance to stay updated of the tasks processed by others.\\\\ To sum up we could say that it was a successfully first project phase.\\Nevertheless there are a few user stories which have been planned for this phase but couldn`t be processed, due to missing time. To those stories belong the implementation of the WebApp. Some user stories could have been processed partly which means they need to be finalized in the next phase. Those are for example data profiling tasks and initialize Graphhopper properly. 
Furthermore it is planned to do the analytics and prediction part in the following phase. This includes to perform analytic tasks with Hadoop, e. g. which routes in London are used most frequented at which time?
Moreover prediction steps should be made e. g. what is the amount of bikes to be rented out at a certain station tomorrow morning?
All those user stories and many more are waiting for us in the following project phase.
