% vim:ft=tex

\section{Hourly Prediction}

\subsection{Data Preparation}

% Sliding windows, ...
% Aggregation stuff...

\subsubsection{Holidays}

To add the bank holidays are day-based, so they should be set on a 24 hour windows.
However, fixing the bank holidays from midnight to midnight the next day will not
be the best solution as people might consider the evening of a bank holiday the same
way as they do for normal week day, while the evening of the day before will be more
interesting. Indeed, when people want to go out in the evening and go to bed late,
they will prefer doing that when they don't have to wake up early in the morning,
thus they may be more likely to use a bike the end of the day before the bank
holiday than of the day itself.

This is why we decided to test the accuracy of the prediction placing bank holidays
from 6pm the day before to 6pm the day itself.

% TODO: accuracies
The accuracy of the overall model on the testing data using the bank-holidays
starting at 6pm is 0.942942. When not using this, we get a lower accuracy of
0.9419142.
% TODO: RMSE ?

\subsection{Learning and Prediction}

For the learning part, we used the same algorithm as described in~\ref{data_prediction}.
We trained twenty-four models, one per future hour to predict.
For each model, we only use the past and current data to train that we match to
the future expected number of rented bike, no other future data is used.

We used the sliding-windows hourly based data over 48 hours (aggregating per slice
of 6 hours after the first 24 hours).
% TODO: add prediction accuracy
On the graph below, you can see several randomly selected days in the testing set
starting at midnight and predicting for the whole day. The title above the graph
indicate the day used, the actual expected value is in red and the predicted one
is in blue.
% TODO: add image of the prediction

As we can see and considering the measured accuracy, we can see that we can predict
quite well the amount of rented bikes for the following 24 hours based on the data of
the previous 48 hours.
